\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-11-28 manuscript.tex
Start adding more detail on problems with Euler angles and quaternions

\section{Experiment on Hexrotor UAV}

>>>>

% Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2001,bate1971,wertz1978}.
For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2001}.
In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
However, the choice of attitude parameterization plays a critical role in control design and the resulting motion of the system.

% singularities and the problems involved with using Euler angles
Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
A general rotation is decomposed as the sequence of three rotations.

% discuss what a singularitly in the euler angle actually means (infinite angular velocity) and divide by zero condition
% show common euler angle sequences

% discuss the unwinding phenomenon with quaternions
\section{Experiment on Hexrotor UAV}
